HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

Here is \XXX{another} example with a missing linker: the source \equo{However,
this review\dots} was translated as \equo{Diese
Überprüfung\dots} (lit. \equo{This review}). The omission is not by HMEANT at
all.

@@

In HMEANT, the alignment between the (reference and candidate) structures is a key
part of the manual annotation. If the alignment cannot be created, the candidate
translation is heavily penalized in score.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that sometimes, the structures of the reference and candidate
translations diverge without any good reason, for instance due to a different
interpretation of a PP-attachment, the verb can have one additional modifier in
one of the structures. It would be desirable to allow updates to the structural
annotations also at the alignment stage
to avoid unduly penalization due to such a spurious diverge.
The same issue was observed by HMEANT authors themselves
\parcite{lo:wu:reliability:2014}:
the 
inter-annotator agreement on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.

>>>>

Here is \XXX{another} example with a missing linker: the source \equo{However,
this review\dots} was translated as \equo{Diese
\"Uberpr\"ufung\dots} (lit. \equo{This review}). The omission is not by HMEANT at
all.

@@

In HMEANT, the alignment between the (reference and candidate) structures is a key
part of the manual annotation. If the alignment cannot be created, the candidate
translation is heavily penalized in score.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that sometimes, the structures of the reference and candidate
translations diverge without any good reason, for instance due to a different
interpretation of a PP-attachment, the verb can have one additional modifier in
one of the structures. It would be desirable to allow updates to the structural
annotations also at the alignment stage
to avoid unduly penalization due to such a spurious divergence.
The same issue was observed by HMEANT authors themselves
\parcite{lo:wu:reliability:2014}:
the 
inter-annotator agreement on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.
